---
title: "Triangle Regional Model 2020 Highway Metrics"
author: "Triangle Regional Model Service Bureau"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    storyboard: true
    theme:
       version: 5
   
---




```{r setup, include=FALSE}
library(flexdashboard)
library(xlsx)
library(readxl)
library(sf)
library(leaflet)
library(rgdal)
library(sp)
library(ggplot2)
library(tcadr)
library(caliperR)
library(tcadr)
library(janitor)
library(data.table)
library(dplyr)
library(ggpmisc)
library(plotly)
library(data.table)
library(knitr)
library(scales)


temp <-  read_tcad("C:/Work/Jake/scenario_links.bin") %>%
  filter(Total_Flow_Daily > 0) %>%
  select(ID, RoadName, HCMType, DailyCount, Total_Flow_Daily, Total_VMT_Daily, Total_Delay_Daily, County, Max_VOC_PM, Max_VOC_AM, AreaType, MPO,Tot_Flow_AM, Tot_Flow_PM, Total_VHT_Daily)

g2_geo <-  st_read("C:/Work/Jake/scenario_links.shp")

g2_geo <- g2_geo %>%
  filter(g2_geo$ID %in% temp$ID)

g2 <- cbind(temp, g2_geo)



g2$County <- tolower(g2$County)



temp <- read_tcad("C:/Work/Jake/scenario_se.bin") %>%
  filter(Type !="External")

get_counties <-read_tcad("C:/Work/Jake/master_tazs.bin") %>% select(TAZ = ID,  County) 

se_2020 <- merge(temp, get_counties)

se_2020$County <- tolower(se_2020$County)

##  
  
##v <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/Full Model Runs/Original TRMv6.2_2016/Input/Highway/Hwy Line.shp") 

##Add VMT field
##v$ToT_VMT <- (v$ABAMVMT+ v$ABMDVMT+ v$ABNTVMT+ v$ABPMVMT+v$BAAMVMT+v$BAMDVMT+ v$BANTVMT+ v$BAPMVMT)


##get rid of NA values, set to zero:

##v[is.na(v)]<-0

##v$COUNTY <- tolower(v$COUNTY)


##Add Daily Counts file: 
##v_counts <- read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/Full Model Runs/Original TRMv6.2_2016/EvalModule/TRM6_Count_2016_Observed.bin") %>%
##  select(ID, Daily_Counts=Daily.Counts)


##Final TRMv6.2 line layer with counts
##add_counts <- left_join(v, v_counts)

g2 <- st_as_sf(g2)



TLHighway <- g2 %>%
  filter(HCMType=="TLHighway")

TLHighway <- st_as_sf(TLHighway)

MajorCollector <- g2 %>%
  filter(HCMType=="MajorCollector")

MajorCollector <- st_as_sf(MajorCollector)

Collector <- g2 %>%
  filter(HCMType=="Collector")

Collector <- st_as_sf(Collector)

MLHighway <- g2 %>%
  filter(HCMType=="MLHighway")

MLHighway <- st_as_sf(MLHighway)

MajorArterial <- g2 %>%
  filter(HCMType=="MajorArterial")

MajorArterial <- st_as_sf(MajorArterial)

Arterial <- g2 %>%
  filter(HCMType=="Arterial")

Arterial <- st_as_sf(Arterial)

Freeway <- g2 %>%
  filter(HCMType=="Freeway")

Freeway <- st_as_sf(Freeway)


```


Highway Assignment Maps {.storyboard data-icon="ion-android-globe"}
=====================================  



### Daily Volume

```{r echo=FALSE, message=FALSE, warning=FALSE}
#colores <- c('grey', 'lightgreen', 'pink', 'green', 'blue', 'orange', 'red',  'darkred')

bins = c(0,2500,5000,10000,25000,50000,125000)


volume_pal <- colorBin(palette="YlOrRd", na.color="#808080", domain=g2$Total_Flow_Daily, bins = bins)



vol_map <- leaflet()%>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(-78.86818828690794, 35.90135612029049, zoom = 8.5) %>%

  addPolylines(data=TLHighway,color=~volume_pal(Total_Flow_Daily),  
              popup = paste("Road Name: ", TLHighway$RoadName , "<br>",
                            "Total Flow: ", TLHighway$Total_Flow_Daily
                            ),
              weight = log(TLHighway$Total_Flow_Daily)/5, 
              group="TLHighway") %>%
  
  addPolylines(data=MajorCollector,color=~volume_pal(Total_Flow_Daily),  
              popup = paste("Road Name: ", MajorCollector$RoadName , "<br>",
                            "Total Flow: ", MajorCollector$Total_Flow_Daily
                            ),
              weight = log(MajorCollector$Total_Flow_Daily)/5, 
              group="MajorCollector") %>%
  addPolylines(data=Collector,color=~volume_pal(Total_Flow_Daily),  
              popup = paste("Road Name: ", Collector$RoadName , "<br>",
                            "Total Flow: ", Collector$Total_Flow_Daily
                            ),
              weight = log(Collector$Total_Flow_Daily)/5, 
              group="Collector") %>%
  addPolylines(data=MLHighway,color=~volume_pal(Total_Flow_Daily),  
              popup = paste("Road Name: ", MLHighway$RoadName , "<br>",
                            "Total Flow: ", MLHighway$Total_Flow_Daily
                            ),
              weight = log(MLHighway$Total_Flow_Daily)/4, 
              group="MLHighway") %>%
  
  addPolylines(data=Arterial,color=~volume_pal(Total_Flow_Daily),  
              popup = paste("Road Name: ", Arterial$RoadName , "<br>",
                            "Total Flow: ", Arterial$Total_Flow_Daily
                            ),
              weight = log(Arterial$Total_Flow_Daily)/4, 
              group="Arterial") %>%
  addPolylines(data=MajorArterial,color=~volume_pal(Total_Flow_Daily),  
              popup = paste("Road Name: ", MajorArterial$RoadName , "<br>",
                            "Total Flow: ", MajorArterial$Total_Flow_Daily
                            ),
              weight = log(MajorArterial$Total_Flow_Daily)/4, 
              group="MajorArterial") %>%
  addPolylines(data=Freeway,color=~volume_pal(Total_Flow_Daily),  
              popup = paste("Road Name: ", Freeway$RoadName , "<br>",
                            "Total Flow: ", Freeway$Total_Flow_Daily
                            ),
              weight = log(Freeway$Total_Flow_Daily)/3, 
              group="Freeway") %>%


      addLegend("bottomright",
            pal=volume_pal,
            value=g2$Total_Flow_Daily,
        #  group="Freeways",
            title="Volume") %>%
  

  
  

  
  addLayersControl(overlayGroups = c("TLHighway", "MajorCollector", "Collector", "MLHighway", "Arterial","MajorArterial",'Freeway'),
                   options = layersControlOptions(collapsed = TRUE))

896
vol_map  %>%hideGroup("TLHighway") %>%hideGroup("MajorCollector") %>% hideGroup("Collector")
```

***

The TRMG2 2020 base year highway assignment by time of day are presented here. Click the layers button to select HCMType for more focused viewing. 



### PM Volume

```{r echo=FALSE, message=FALSE, warning=FALSE}


bins = c(0,2500,5000,10000,15000,20000,30000)


volume_pal <- colorBin(palette="YlOrRd", na.color="#808080", domain=g2$Tot_Flow_PM, bins = bins)


vol_map <- leaflet()%>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(-78.86818828690794, 35.90135612029049, zoom = 8.5) %>%  
  addPolylines(data=TLHighway,color=~volume_pal(Tot_Flow_PM),  
              popup = paste("Road Name: ", TLHighway$RoadName , "<br>",
                            "Total PM Flow: ", TLHighway$Tot_Flow_PM
                            ),
              weight = log(TLHighway$Tot_Flow_PM)/5, 
              group="TLHighway") %>%
  
  addPolylines(data=MajorCollector,color=~volume_pal(Tot_Flow_PM),  
              popup = paste("Road Name: ", MajorCollector$RoadName , "<br>",
                            "Total PM Flow: ", MajorCollector$Tot_Flow_PM
                            ),
              weight = log(MajorCollector$Tot_Flow_PM)/5, 
              group="MajorCollector") %>%
  addPolylines(data=Collector,color=~volume_pal(Tot_Flow_PM),  
              popup = paste("Road Name: ", Collector$RoadName , "<br>",
                            "Total PM Flow: ", Collector$Tot_Flow_PM
                            ),
              weight = log(Collector$Tot_Flow_PM)/5, 
              group="Collector") %>%
  addPolylines(data=MLHighway,color=~volume_pal(Tot_Flow_PM),  
              popup = paste("Road Name: ", MLHighway$RoadName , "<br>",
                            "Total PM Flow: ", MLHighway$Tot_Flow_PM
                            ),
              weight = log(MLHighway$Tot_Flow_PM)/4, 
              group="MLHighway") %>%
  
  addPolylines(data=Arterial,color=~volume_pal(Tot_Flow_PM),  
              popup = paste("Road Name: ", Arterial$RoadName , "<br>",
                            "Total PM Flow: ", Arterial$Tot_Flow_PM
                            ),
              weight = log(Arterial$Tot_Flow_PM)/4, 
              group="Arterial") %>%
  addPolylines(data=MajorArterial,color=~volume_pal(Tot_Flow_PM),  
              popup = paste("Road Name: ", MajorArterial$RoadName , "<br>",
                            "Total PM Flow: ", MajorArterial$Tot_Flow_PM
                            ),
              weight = log(MajorArterial$Tot_Flow_PM)/4, 
              group="MajorArterial") %>%
  addPolylines(data=Freeway,color=~volume_pal(Tot_Flow_PM),  
              popup = paste("Road Name: ", Freeway$RoadName , "<br>",
                            "Total PM Flow: ", Freeway$Tot_Flow_PM
                            ),
              weight = log(Freeway$Tot_Flow_PM)/3, 
              group="Freeway") %>%


      addLegend("bottomright",
            pal=volume_pal,
            value=g2$Tot_Flow_PM,
         #   group="Freeways AM",
            title="PM Volume") %>%
  
  

  
  
  addLayersControl(overlayGroups = c("TLHighway", "MajorCollector", "Collector", "MLHighway", "Arterial","MajorArterial",'Freeway'),
                   options = layersControlOptions(collapsed = TRUE))


vol_map  %>%hideGroup("TLHighway") %>%hideGroup("MajorCollector") %>% hideGroup("Collector")
```






### AM Volume

```{r echo=FALSE, message=FALSE, warning=FALSE}

bins = c(0,2500,5000,7500,10000,15000,20000)

volume_pal <- colorBin(palette="YlOrRd", na.color="#808080", domain=g2$Tot_Flow_AM, bins = bins)


vol_map <- leaflet()%>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(-78.86818828690794, 35.90135612029049, zoom = 8.5) %>% 

  addPolylines(data=TLHighway,color=~volume_pal(Tot_Flow_AM),  
              popup = paste("Road Name: ", TLHighway$RoadName , "<br>",
                            "Total AM Flow: ", TLHighway$Tot_Flow_AM
                            ),
              weight = log(TLHighway$Tot_Flow_AM)/5, 
              group="TLHighway") %>%
  
  addPolylines(data=MajorCollector,color=~volume_pal(Tot_Flow_AM),  
              popup = paste("Road Name: ", MajorCollector$RoadName , "<br>",
                            "Total AM Flow: ", MajorCollector$Tot_Flow_AM
                            ),
              weight = log(MajorCollector$Tot_Flow_AM)/5, 
              group="MajorCollector") %>%
  addPolylines(data=Collector,color=~volume_pal(Tot_Flow_AM),  
              popup = paste("Road Name: ", Collector$RoadName , "<br>",
                            "Total AM Flow: ", Collector$Tot_Flow_AM
                            ),
              weight = log(Collector$Tot_Flow_AM)/5, 
              group="Collector") %>%
  addPolylines(data=MLHighway,color=~volume_pal(Tot_Flow_AM),  
              popup = paste("Road Name: ", MLHighway$RoadName , "<br>",
                            "Total AM Flow: ", MLHighway$Tot_Flow_AM
                            ),
              weight = log(MLHighway$Tot_Flow_AM)/4, 
              group="MLHighway") %>%
  
  addPolylines(data=Arterial,color=~volume_pal(Tot_Flow_AM),  
              popup = paste("Road Name: ", Arterial$RoadName , "<br>",
                            "Total AM Flow: ", Arterial$Tot_Flow_AM
                            ),
              weight = log(Arterial$Tot_Flow_AM)/4, 
              group="Arterial") %>%
  addPolylines(data=MajorArterial,color=~volume_pal(Tot_Flow_AM),  
              popup = paste("Road Name: ", MajorArterial$RoadName , "<br>",
                            "Total AM Flow: ", MajorArterial$Tot_Flow_AM
                            ),
              weight = log(MajorArterial$Tot_Flow_AM)/4, 
              group="MajorArterial") %>%
  addPolylines(data=Freeway,color=~volume_pal(Tot_Flow_AM),  
              popup = paste("Road Name: ", Freeway$RoadName , "<br>",
                            "Total AM Flow: ", Freeway$Tot_Flow_AM
                            ),
              weight = log(Freeway$Tot_Flow_AM)/3, 
              group="Freeway") %>%


      addLegend("bottomright",
            pal=volume_pal,
            value=g2$Tot_Flow_AM,
         #   group="Freeways AM",
            title="AM Volume") %>%
  
  

  
  addLayersControl(overlayGroups = c( "TLHighway", "MajorCollector", "Collector", "MLHighway", "Arterial","MajorArterial",'Freeway'),
                   options = layersControlOptions(collapsed = TRUE))


vol_map  %>%hideGroup("TLHighway") %>%hideGroup("MajorCollector") %>% hideGroup("Collector")
```












Capacity & Congestion {.storyboard data-icon="fa-clock"}
=====================================  

### Congested Time
 

```{r echo=FALSE, message=FALSE, warning=FALSE}

congested_bins <- c(0, 5, 10, 50, 100, 250, 500)

congested_pal <- colorBin(
  palette = "YlOrRd", na.color = "#808080",
  bins=congested_bins,
  domain = g2$Total_Delay_Daily)



cong_map <- leaflet()%>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(-78.86818828690794, 35.90135612029049, zoom = 8.5) %>%  
  addPolylines(data=TLHighway,color=~congested_pal(Total_Delay_Daily),  
              popup = paste("Road Name: ", TLHighway$RoadName , "<br>",
                            "Total Delay: ", TLHighway$Total_Delay_Daily
                            ),
              group="TLHighway") %>%
  
  addPolylines(data=MajorCollector,color=~congested_pal(Total_Delay_Daily),  
              popup = paste("Road Name: ", MajorCollector$RoadName , "<br>",
                            "Total Delay: ", MajorCollector$Total_Delay_Daily
                            ),
             # size=MajorCollector$Total_Flow_Daily,
              group="MajorCollector") %>%
  addPolylines(data=Collector,color=~congested_pal(Total_Delay_Daily),  
              popup = paste("Road Name: ", Collector$RoadName , "<br>",
                            "Total Delay: ", Collector$Total_Delay_Daily
                            ),
              group="Collector") %>%
  addPolylines(data=MLHighway,color=~congested_pal(Total_Delay_Daily),  
              popup = paste("Road Name: ", MLHighway$RoadName , "<br>",
                            "Total Delay: ", MLHighway$Total_Delay_Daily
                            ),
              group="MLHighway") %>%
  
  addPolylines(data=Arterial,color=~congested_pal(Total_Delay_Daily),  
              popup = paste("Road Name: ", Arterial$RoadName , "<br>",
                            "Total Delay: ", Arterial$Total_Delay_Daily
                            ),
              group="Arterial") %>%
  addPolylines(data=MajorArterial,color=~congested_pal(Total_Delay_Daily),  
              popup = paste("Road Name: ", MajorArterial$RoadName , "<br>",
                            "Total Delay: ", MajorArterial$Total_Delay_Daily
                            ),
              group="MajorArterial") %>%
  addPolylines(data=Freeway,color=~congested_pal(Total_Delay_Daily),  
              popup = paste("Road Name: ", Freeway$RoadName , "<br>",
                            "Total Delay: ", Freeway$Total_Delay_Daily
                            ),
              group="Freeway") %>%



      addLegend("bottomright",
            pal=congested_pal,
            value=g2$Total_Delay_Daily,
         #   group="Freeways AM",
            title="Delay (Hours)") %>%

  addLayersControl(overlayGroups = c("TLHighway", "MajorCollector", "Collector", "MLHighway", "Arterial","MajorArterial",'Freeway'),
                   options = layersControlOptions(collapsed = TRUE))


cong_map  %>%hideGroup("TLHighway") %>%hideGroup("MajorCollector") %>% hideGroup("Collector") %>%hideGroup("MajorArterial")
```



***

While some links in the model are uni-directional (one-way) others are bi-directional. Congested Time represents total delay in both directions for each link. 

### AM VOC

```{r echo=FALSE, message=FALSE, warning=FALSE}

congested_bins <- c(0,.4,.8,1.2,1.6)

congested_pal <- colorBin(
  palette = c("#B2182B", "#F4A582", "#D1E5F0", "#92C5DE"), na.color = "#808080",
  bins=congested_bins,
  domain = g2$Max_VOC_AM,
  reverse=TRUE)


cong_map <- leaflet()%>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(-78.86818828690794, 35.90135612029049, zoom = 8.5) %>%  
  addPolylines(data=TLHighway,color=~congested_pal(Max_VOC_AM),  
              popup = paste("Road Name: ", TLHighway$RoadName , "<br>",
                            "AM VOC: ", TLHighway$Max_VOC_AM
                            ),
              group="TLHighway") %>%
  
  addPolylines(data=MajorCollector,color=~congested_pal(Max_VOC_AM),  
              popup = paste("Road Name: ", MajorCollector$RoadName , "<br>",
                            "AM VOC: ", MajorCollector$Max_VOC_AM
                            ),
             # size=MajorCollector$Total_Flow_Daily,
              group="MajorCollector") %>%
  addPolylines(data=Collector,color=~congested_pal(Max_VOC_AM),  
              popup = paste("Road Name: ", Collector$RoadName , "<br>",
                            "AM VOC: ", Collector$Max_VOC_AM
                            ),
              group="Collector") %>%
  addPolylines(data=MLHighway,color=~congested_pal(Max_VOC_AM),  
              popup = paste("Road Name: ", MLHighway$RoadName , "<br>",
                            "AM VOC: ", MLHighway$Max_VOC_AM
                            ),
              group="MLHighway") %>%
  
  addPolylines(data=Arterial,color=~congested_pal(Max_VOC_AM),  
              popup = paste("Road Name: ", Arterial$RoadName , "<br>",
                            "AM VOC: ", Arterial$Max_VOC_AM
                            ),
              group="Arterial") %>%
  addPolylines(data=MajorArterial,color=~congested_pal(Max_VOC_AM),  
              popup = paste("Road Name: ", MajorArterial$RoadName , "<br>",
                            "AM VOC: ", MajorArterial$Max_VOC_AM
                            ),
              group="MajorArterial") %>%
  addPolylines(data=Freeway,color=~congested_pal(Max_VOC_AM),  
              popup = paste("Road Name: ", Freeway$RoadName , "<br>",
                            "AM VOC: ", Freeway$Max_VOC_AM
                            ),
              group="Freeway") %>%



      addLegend("bottomright",
            pal=congested_pal,
            value=g2$Max_VOC_AM,
         #   group="Freeways AM",
            title="AM VOC") %>%
  
  addLayersControl(overlayGroups = c("TLHighway", "MajorCollector", "Collector", "MLHighway", "Arterial","MajorArterial",'Freeway'),
                   options = layersControlOptions(collapsed = TRUE))


cong_map  %>%hideGroup("TLHighway") %>%hideGroup("MajorCollector") %>% hideGroup("Collector")
```



***

Volume-to-Capacity is a common metric to measure the usage and capacity of a particular roadway. V/C ratios are a critical input in determining the Level of service (LOS), a qualitative metric graded A to F, representing the best to worst operating conditions. 


### PM VOC

```{r echo=FALSE, message=FALSE, warning=FALSE}

congested_bins <- c(0,.4,.8,1.2,1.6)

congested_pal <- colorBin(
  palette = c("#B2182B", "#F4A582", "#D1E5F0", "#92C5DE"), na.color = "#808080",
  bins=congested_bins,
  domain = g2$Max_VOC_PM,
  reverse=TRUE)




cong_map <- leaflet()%>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(-78.86818828690794, 35.90135612029049, zoom = 8.5) %>%  
  addPolylines(data=TLHighway,color=~congested_pal(Max_VOC_PM),  
              popup = paste("Road Name: ", TLHighway$RoadName , "<br>",
                            "PM VOC: ", TLHighway$Max_VOC_PM
                            ),
              group="TLHighway") %>%
  
  addPolylines(data=MajorCollector,color=~congested_pal(Max_VOC_PM),  
              popup = paste("Road Name: ", MajorCollector$RoadName , "<br>",
                            "PM VOC: ", MajorCollector$Max_VOC_PM
                            ),
             # size=MajorCollector$Total_Flow_Daily,
              group="MajorCollector") %>%
  addPolylines(data=Collector,color=~congested_pal(Max_VOC_PM),  
              popup = paste("Road Name: ", Collector$RoadName , "<br>",
                            "PM VOC: ", Collector$Max_VOC_PM
                            ),
              group="Collector") %>%
  addPolylines(data=MLHighway,color=~congested_pal(Max_VOC_PM),  
              popup = paste("Road Name: ", MLHighway$RoadName , "<br>",
                            "PM VOC: ", MLHighway$Max_VOC_PM
                            ),
              group="MLHighway") %>%
  
  addPolylines(data=Arterial,color=~congested_pal(Max_VOC_PM),  
              popup = paste("Road Name: ", Arterial$RoadName , "<br>",
                            "PM VOC: ", Arterial$Max_VOC_PM
                            ),
              group="Arterial") %>%
  addPolylines(data=MajorArterial,color=~congested_pal(Max_VOC_PM),  
              popup = paste("Road Name: ", MajorArterial$RoadName , "<br>",
                            "PM VOC: ", MajorArterial$Max_VOC_PM
                            ),
              group="MajorArterial") %>%
  addPolylines(data=Freeway,color=~congested_pal(Max_VOC_PM),  
              popup = paste("Road Name: ", Freeway$RoadName , "<br>",
                            "PM VOC: ", Freeway$Max_VOC_PM
                            ),
              group="Freeway") %>%



      addLegend("bottomright",
            pal=congested_pal,
            value=g2$Max_VOC_PM,
         #   group="Freeways AM",
            title="PM VOC") %>%
  
  
  addLayersControl(overlayGroups = c("TLHighway", "MajorCollector", "Collector", "MLHighway", "Arterial","MajorArterial",'Freeway'),
                   options = layersControlOptions(collapsed = TRUE))


cong_map  %>%hideGroup("TLHighway") %>%hideGroup("MajorCollector") %>% hideGroup("Collector") %>%hideGroup("MajorArterial")


```











County Statistics {.storyboard data-icon="ion-stats-bars"}
=====================================  




### Population

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(scales)

county_data <- se_2020 %>%
  group_by(County) %>%
  summarize(
   Population = sum(HH_POP, na.rm=T),
    Households = sum(HH, na.rm=T)#,
   # K12 = sum(K12, na.rm=T),
   # 'College Off-Campus' = sum(StudGQ_NCSU, StudGQ_UNC,StudGQ_DUKE,StudGQ_NCCU, CollegeOn, na.rm=T),
   # 'College On-Campus' = sum(CollegeOff, na.rm=T)
      )

temp <- melt(as.data.table(county_data))



p <- ggplot(data=temp, aes(x=County, y=value, fill = variable)) +geom_bar(stat='identity', position='dodge') + theme_classic() + xlab('')+ ylab('')+ ggtitle("Demographic County Totals")+ theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)+ labs(fill = "")

ggplotly(p)





```


### Education
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(scales)

county_data <- se_2020 %>%
  group_by(County) %>%
  summarize(
   # Population = sum(HH_POP, na.rm=T),
    #Households = sum(HH, na.rm=T)#,
   K12 = sum(K12, na.rm=T),
    'College Off-Campus' = sum(StudGQ_NCSU, StudGQ_UNC,StudGQ_DUKE,StudGQ_NCCU, CollegeOn, na.rm=T),
    'College On-Campus' = sum(CollegeOff, na.rm=T)
      )

temp <- melt(as.data.table(county_data))



p <- ggplot(data=temp, aes(x=County, y=value, fill = variable)) +geom_bar(stat='identity', position='dodge') + theme_classic() + xlab('')+ ylab('')+ ggtitle("Education County Totals")+ theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)+ labs(fill = "")

ggplotly(p)





```

### Employment

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(scales)

county_data <- se_2020 %>%
  group_by(County) %>%
  summarize(
   # 'Total Employment' = sum(Industry, Office, Service_RateLow, Service_RateHigh, Retail, na.rm=T),
    'Industry' = sum(Industry, na.rm=T),
    'Office' = sum(Office, na.rm=T),
    'Service Rate Low'= sum(Service_RateLow, na.rm=T),
    'Service Rate High' = sum(Service_RateHigh, na.rm=T),
    Retail = sum(Retail, na.rm=T)
      )

temp <- melt(as.data.table(county_data))



p <- ggplot(data=temp, aes(x=County, y=value, fill = variable)) +geom_bar(stat='identity', position='dodge') + theme_classic() + xlab('')+ ylab('')+ ggtitle("Employment County Totals")+ theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)+ labs(fill = "")

ggplotly(p)





```







### Total Trips


```{r echo=FALSE, message=FALSE, warning=FALSE}

flow_flip <- g2 %>%
  st_drop_geometry() %>%
  group_by(County) %>%
  filter(DailyCount > 0) %>%
  filter(County != "") %>% ##filters empty space for tagged links with no counties 
  summarise(
    Total_Flow = sum(Total_Flow_Daily, na.rm=T)) %>%
  arrange(County)%>%
  mutate(Total_Flow = round(Total_Flow, 0))


p <- ggplot(data=flow_flip, aes(x=County, y=Total_Flow)) +geom_bar(stat='identity',fill="orange") + theme_classic() + xlab('')+ ylab('')+  theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)

ggplotly(p) 



```


### VHT


```{r echo=FALSE, message=FALSE, warning=FALSE}

vht_flip <- g2 %>%  
  st_drop_geometry()%>%
  group_by(County) %>%
  filter(DailyCount > 0) %>%
  filter(County != "") %>% ##filters empty space for tagged links with no counties 
  summarise(
    Total_VHT = sum(Total_VHT_Daily, na.rm=T)) %>%
  arrange(County)%>%
  mutate(Total_VHT = round(Total_VHT, 0))



p <- ggplot(data=vht_flip, aes(x=County, y=Total_VHT)) +geom_bar(stat='identity',fill="blue") + theme_classic() + xlab('')+ ylab('')+  theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)

ggplotly(p) 



```


### VMT


```{r echo=FALSE, message=FALSE, warning=FALSE}

vmt_flip <- g2 %>%  
  st_drop_geometry()%>%
  group_by(County) %>%
  filter(DailyCount > 0) %>%
  filter(County != "") %>% ##filters empty space for tagged links with no counties 
  summarise(
    Total_VMT = sum(Total_VMT_Daily, na.rm=T)) %>%
  arrange(County)%>%
  mutate(Total_VMT = round(Total_VMT, 0))





p <- ggplot(data=vmt_flip, aes(x=County, y=Total_VMT)) +geom_bar(stat='identity',fill="grey") + theme_classic() + xlab('')+ ylab('')+ theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)+ labs(fill = "")

ggplotly(p) 



```




### Trip Ratios

```{r echo=FALSE, message=FALSE, warning=FALSE}

county_data <- se_2020 %>%
  group_by(County) %>%
  summarize(
    Population = sum(HH_POP, na.rm=T),
    'Employment' = sum(Industry, Office, Service_RateLow, Service_RateHigh, Retail, na.rm=T),
    Households = sum(HH, na.rm=T),
    K12 = sum(K12, na.rm=T),
    'College Off-Campus' = sum(StudGQ_NCSU, StudGQ_UNC,StudGQ_DUKE,StudGQ_NCCU, CollegeOn, na.rm=T),
    'College On-Campus' = sum(CollegeOff, na.rm=T)
      )

temp <- merge(county_data, flow_flip) %>%
  mutate('Trips/Person' = round(Total_Flow/Population, 1),
         'Trips/HH' = round(Total_Flow/Households, 1),
         'Trips/Job' = round(Total_Flow/Employment, 1)) %>%
  select(County, 'Trips/Person', 'Trips/HH','Trips/Job')

temp <- melt(as.data.table(temp))



p <- ggplot(data=temp, aes(x=County, y=value, fill = variable)) +geom_bar(stat='identity', position='dodge') + theme_classic() + xlab('')+ ylab('')+ ggtitle("County Level Total Trips")+ theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)+ labs(fill = "")

ggplotly(p) 

```



### VMT

```{r echo=FALSE, message=FALSE, warning=FALSE}

temp <- merge(county_data, vmt_flip) %>%
  mutate('VMT/Person' = round(Total_VMT/Population, 1),
         'VMT/HH' = round(Total_VMT/Households, 1),
         'VMT/Job' = round(Total_VMT/Employment, 1)) %>%
  select(County, 'VMT/Person', 'VMT/HH','VMT/Job')

temp <- melt(as.data.table(temp))



p <- ggplot(data=temp, aes(x=County, y=value, fill = variable)) +geom_bar(stat='identity', position='dodge') + theme_classic() + xlab('')+ ylab('')+ ggtitle("County Level Total VMT")+ theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)+ labs(fill = "")

ggplotly(p) 

```




### VHT

```{r echo=FALSE, message=FALSE, warning=FALSE}

temp <- merge(county_data, vht_flip) %>%
  mutate('VHT/Person' = round(Total_VHT/Population,1),
         'VHT/HH' = round(Total_VHT/Households, 1),
         'VHT/Job' = round(Total_VHT/Employment, 1)) %>%
  select(County, 'VHT/Person', 'VHT/HH','VHT/Job')

temp <- melt(as.data.table(temp))



p <- ggplot(data=temp, aes(x=County, y=value, fill = variable)) +geom_bar(stat='identity', position='dodge') + theme_classic() + xlab('')+ ylab('')+ ggtitle("County Level Total VHT")+ theme(axis.text.x=element_text(angle = -45, hjust = 0))+ scale_y_continuous(labels=comma)+ labs(fill = "")

ggplotly(p) 

```



Overview {.storyboard}
=====================================  

**Acronyms**

1. VMT: Vehicle Miles Traveled

2. VHT: Vehicle Hours Traveled

3. VOC: Volume-over-Capacity ratio










